General constraints on magic distillation protocols from statistical mechanics

### 2021-04-21 magic_paper.tex
minor adjustment

The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
For the noisy Strange state, the max-thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}. 
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by majorisation, mana and the line $1-\epsilon$ (tightest bound of max--thauma) are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
    Majorisation provides stricter rates than the global mana and max--thauma bounds.
    }
    \label{fig:distill_bounds}
\end{figure}

I include in~\cref{fig:test} the purification of Norrell states and the purification of $T$ states.\nick{Need to include numerical majorization curves to compare, extend noise range.}

>>>>

The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\mana{\rho_{\rm{S}}(\epsilon)}}{\mana{\rho_{\rm{S}}(0)}} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
For the noisy Strange state, the max--thauma bound coincides with the mana bound, and are both looser than the majorization bound we derived via the first elbow constraint as illustrated in~\cref{fig:distill_bounds}. 
\begin{figure}[t]
    \centering
    \includegraphics[scale=0.45]{figs/distill_bounds.pdf}
    \caption{\textbf{Distillation bounds in the unital fragment.} Distillation bounds obtained by the first elbow majorisation constraint, mana and max--thauma are plotted for $\epsilon' = 0$, up to noise level $\epsilon = 3/7$.
    Majorisation provides stricter rates than the global mana and max--thauma bounds.
    }
    \label{fig:distill_bounds}
\end{figure}

I include in~\cref{fig:test} the mana and max--thauma bounds for the purification of (a) Norrell states and (b) $T$ states.
\nick{Need to include numerical majorization curves to compare, extend noise range.}
